---
title: "README"
output:
  md_document:
    variant: gfm
    toc: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(knitr)
```

# Introduction

This small script allows the management of simple glossaries.

## Dependencies

This script depends on the following packages:

```{r, include=FALSE}
library(magrittr)
library(dplyr)
library(glue)
library(reactable)
```

```{r, eval=FALSE}
library(magrittr)
library(dplyr)
library(glue)
library(reactable)
```

# Use

## Load and create a glossary

```{r}
source("glossary.R")
glossary <- create_glossary()
```

## Add terms in the glossary

```{r}
glossary$add_term(
   "UMI",
   "Unique Molecular Identifier. Each PCR primer is associated to a UMI to identify PCR duplicates when quantifying the transcripts. Therefore the number of counts corresponds to the number of UMI which is the quantification measure per feature."
)
```

Synonyms can also be provided:

```{r}
glossary$add_term(
   "MT",
   "Genes coded by mitochondrial genome. MT (%) corresponds to the percentage of UMI corresponding to mitochondrial genes."
)
glossary$add_synonyms("MT", "MT (%)")
```

## Showing the glossary

- `glossary$get_table()` returns the glossary tibble
- `glossary$view()` shows the glossary in a reactable

## Get definitions

The following function is used to get the definitions of terms of interest.
It's case insensitive and support plurals by default.

```{r}
glossary$get_definitions(c("mt", "UMIs"))
```

In an markdown or html document, the definitions can be shown in tooltips
using the `glossary$get_html_definitions()` function.
For example: <strong>`r glossary$get_html_definitions("UMIs")`</strong>.
CSS style can be customized using the `style` parameter
(Unfortunately, CSS are not rendered in GitHub markdown as it is a part of the
sanitization process).

To make it easier to use in an Rmd document in RStudio this function can
be copied in a function with a shorter name such as:

```{r}
td <- glossary$get_html_definitions
```

And then the following
markdown [snippet](https://support.rstudio.com/hc/en-us/articles/204463668-Code-Snippets)
can be added in RStudio (Edit Snippets button in Global Options -> Code):

```
snippet td
	`r${2} td(${1})`
```
